ODGI: understanding pangenome graphs

### 2021-10-18 manuscript/main.tex
Discussion: minor edits and comments
Note on pggb

@@

(recent) interactive visualization tools?! CITE PANACHE, also indicate that no published tool for interactive exploration of such graphs exist

@@

>>>>

\FIXME{Would it be an idea to put part of pggb in a box and explain steps? That way people can visualize using the toolkit and we can refer to it in the text}

@@

(recent) interactive visualization tools?! CITE PANACHE, also indicate that no published tool for interactive exploration of such graphs exist
\FIXME{mention gfaestus?}

@@

\FIXME{I think we can leave RDF and FAIR out as it does not really relate to performance and ODGI explorations. Cancer, yes, we could state that the tools are applicable to cancer genome exploration as wild variation can be represented :)}
